---
title: "Stability"
output: pdf_document
date: '2022-07-27'

header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
---

Plots of fruit proportion and year for each plant species and site 

```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
library(tidyverse)
#install.packages("broom.mixed")
library(broom.mixed)
library(broom)
#install.packages("lmerTest")
library(lmerTest)
library(dplyr)
library(reshape2)
library(tidyr)
library(ggplot2)
#install.packages("ggeffects")
library(ggeffects)
library(patchwork)
library(ggcorrplot)
library(ggpubr)
library(kableExtra)

Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
Pollinator_Plant<-Pollinator_Plant[,-1]


#Species out
spp_out <- Pollinator_Plant %>%
  group_by(Plant_gen_sp) %>%
  summarise(Unique_Id = n_distinct(Site_ID)) %>%
  filter(Unique_Id == 1) %>%
  select(Plant_gen_sp) %>% pull(Plant_gen_sp)


#Data with species in more than 1 site
Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)

# replace NAs by 0
Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))


# datos sin plant_id (mean de las variables porque hay plantas con 2 indv, otras 3, etc)
pol_plant2=Pollinator_Plant %>%
  group_by(Site_ID,Year, Plant_gen_sp) %>%
  summarise_if(is.numeric, mean)

pol_plant2$Year <- factor(pol_plant2$Year)

plots3 <- pol_plant2 %>%
group_by(Plant_gen_sp) %>%
group_map(~ ggplot(.) + aes(x=Year, y=fruit_proportion, col =factor(Site_ID))+ theme_bw()+geom_point(size = 5,alpha = 0.5)+  theme(axis.title = element_text(size = 20))+ theme(axis.text = element_text(size = 15)) + theme(plot.title = element_text(size = 20)) + theme(legend.text = element_text(size = 13)) + ggtitle(.y[[1]])) 


ggarrange(plots3[[1]],plots3[[2]],plots3[[3]],plots3[[4]],plots3[[5]],plots3[[6]], plots3[[7]],plots3[[8]],plots3[[9]],plots3[[10]],plots3[[11]],plots3[[12]],ncol=3,nrow = 4)

```

\newpage

Plots of seed number and year for each plant species and site 

```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}

plots3_seed <- pol_plant2 %>%
group_by(Plant_gen_sp) %>%
group_map(~ ggplot(.) + aes(x=Year, y=Seeds, col =factor(Site_ID))+ theme_bw()+geom_point(size = 5,alpha = 0.5)+  theme(axis.title = element_text(size = 20))+ theme(axis.text = element_text(size = 15)) + theme(plot.title = element_text(size = 20)) + theme(legend.text = element_text(size = 13)) + ggtitle(.y[[1]])) 


ggarrange(plots3_seed[[1]],plots3_seed[[2]],plots3_seed[[3]],plots3_seed[[4]],plots3_seed[[5]],plots3_seed[[6]],plots3_seed[[7]],plots3_seed[[8]],plots3_seed[[9]],plots3_seed[[10]],plots3_seed[[11]],plots3_seed[[12]],ncol=3,nrow = 4)

```

\newpage

Plots of visitation rate and year for each plant species and site 

```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}

plots3_visitation_rate <- pol_plant2 %>%
group_by(Plant_gen_sp) %>%
group_map(~ ggplot(.) + aes(x=Year, y=visitatio_rate, col =factor(Site_ID))+ theme_bw()+geom_point(size = 5,alpha = 0.5)+  theme(axis.title = element_text(size = 20))+ theme(axis.text = element_text(size = 15)) + theme(plot.title = element_text(size = 20)) + theme(legend.text = element_text(size = 13)) + ggtitle(.y[[1]])) 


ggarrange(plots3_visitation_rate[[1]],plots3_visitation_rate[[2]],plots3_visitation_rate[[3]],plots3_visitation_rate[[4]],plots3_visitation_rate[[5]],plots3_visitation_rate[[6]],plots3_visitation_rate[[7]],plots3_visitation_rate[[8]],plots3_visitation_rate[[9]],plots3_visitation_rate[[10]],plots3_visitation_rate[[11]],plots3_visitation_rate[[12]],ncol=3,nrow = 4)

```


\newpage
For each plant species per site, stability (inverse of the coefficient of variation) of the visitation rate of pollinators (visitation rate calculated like frequency/flower abundance) and also of the fruit proportion and the seed numbers were calculated. Pollinator richness (total and mean) was obtained and furthermore, the log of variance ratio (Lepš et al., 2018) and Loreau & Mazancourt syncrony index were calculated.

Positive values of log var ratio signify synchronization, negative values indicate compensatory dynamics (Lepš et al., 2018).
Loreau & Mazancourt index is standardized between 0 (perfect asynchrony) and 1 (perfect synchrony).

note: NA= one data per year

```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}

# datos por año y sitio para cada sp de planta (sin plant_id)
cv_1Fruit2<-pol_plant2 %>%
  group_by(Plant_gen_sp,Site_ID) %>%
  summarise_at(vars(fruit_proportion),cv_1 <- function(x, ...) {
    ( mean(x, ...)/sd(x, ...) )
  })%>%
  ungroup()

# datos por año y sitio para cada sp de planta (sin plant_id)
cv_1Seed2<-pol_plant2 %>%
  group_by(Plant_gen_sp,Site_ID) %>%
  summarise_at(vars(Seeds),cv_1 <- function(x, ...) {
    ( mean(x, ...)/sd(x, ...) )
  })%>%
  ungroup()

# datos por año y sitio para cada sp de planta (sin plant_id)
cv_1pollinator2<-pol_plant2 %>%
  group_by(Plant_gen_sp,Site_ID) %>%
  summarise_at(vars(visitatio_rate),cv_1 <- function(x, ...) {
    ( mean(x, ...)/sd(x, ...) )
  })%>%
  ungroup()

#  pollinator richness for each plant species per site (Total)
S<-aggregate(richness ~ Plant_gen_sp+Site_ID, data = Pollinator_Plant,FUN = sum)

#suma de la riqueza media por año para cada plant sp y sitio
S2<-aggregate(richness ~ Plant_gen_sp+Site_ID, data = pol_plant2,FUN = sum)


## Synchrony ###

focal<- read.csv("../Data/focal.csv") 
focal<-focal[,-1]


focal_0 <- focal[!(focal$Pollinator_gen_sp == "NA NA"),] #eliminar polinizadores NA NA

#Data with species in more than 1 site
focal_0 = focal_0 %>% filter(!Plant_gen_sp %in% spp_out)

focal_0<-subset(focal_0, Plant_gen_sp != 'Ulex australis') #remove ulex
plant_polli<-data.frame(focal_0[,c(1,2,6,29,30)])


df.result <- left_join(Pollinator_Plant, plant_polli, c('Plant_gen_sp', 'Site_ID','Year','plant_id'))
df.result1<-data.frame(df.result[,c(1,2,3,4,25)])
df.result2 <- dcast(df.result, formula = Site_ID + Year +plant_id+Plant_gen_sp ~ Pollinator_gen_sp)

# sin plant_id
prueba=df.result2 %>%
  group_by(Site_ID,Year, Plant_gen_sp) %>%
  summarise_if(is.numeric, sum) 

# log variance ratio (Lepš et al., 2018)
#log (Var over the Sum of abundances of all species over time/ Sum of the variance of each species over time)
# Positive values of log var ratio signify synchronization, negative values indicate compensatory dynamics

log_VR <- function(x){
  out <- log((var(rowSums(x))) / (sum(apply(x, MARGIN = 2, FUN = var)))) 
  out                               
}

# un dato por sp planta, sitio y año (sin plant_id)
syn_2=prueba%>% 
  group_by(Plant_gen_sp,Site_ID)%>% 
  do(log_VR=log_VR(.[4:127]))


# Loreau & Mazancourt syncrony index
#sum of the tempotral covariances of all species / sum of sqrt of the variances squared
syncLM <- function(x){
  out <- (sum(cov(x))) / (sum(sqrt(diag(cov(x))))^2)
  out
}

# un dato por sp planta, sitio y año (sin plant_id)
syn_LM2=prueba%>% 
  group_by(Plant_gen_sp,Site_ID)%>% 
  do(syncLM=syncLM(.[4:127]))


# join tables 
full2=full_join(cv_1Fruit2, cv_1Seed2, by = c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., cv_1pollinator2, by=c('Plant_gen_sp', 'Site_ID')) %>%
  full_join (., S, by=c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., S2, by=c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., syn_2, by=c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., syn_LM2, by=c('Plant_gen_sp', 'Site_ID'))%>%
  rename(cv_1_fruit=fruit_proportion, cv_1_seed=Seeds,   cv_1_visitation=visitatio_rate,S_total=richness.x, S_mean=richness.y)


full2$log_VR <- unlist(full2$log_VR)
full2$syncLM <- unlist(full2$syncLM)

full2 %>% 
    kable("latex",booktabs = TRUE, digits =  4,longtable = T,linesep = "")%>%
  kable_styling(font_size = 8,full_width = F, position="left")
```



Correlation 
```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}

tr2<-full2 %>% select(cv_1_fruit, cv_1_seed,cv_1_visitation,S_total, S_mean)

## Replace Inf and -Inf with NA
tr2[is.na(tr2) | tr2 == "Inf"] <- 0 
tr2[is.na(tr2) | tr2 == "-Inf"] <- 0 

tr2 <- mutate_all(tr2, ~replace(., is.na(.), 0))

cr=cor(tr2)

cr %>% 
    kable("latex",booktabs = TRUE, digits =  4)

```


\newpage

\blandscape


```{r, echo=FALSE, warning=FALSE,message=FALSE, figures-side,fig.height = 13,fig.width=18, out.width="100%",fig.fullwidth=TRUE}

library(tidyverse)
library(broom.mixed)
library(broom)
library(lmerTest)
library(dplyr)
library(knitr)
library(kableExtra)
library(patchwork)
library(ggcorrplot)
library(ggpubr)


# correlacion con nuevos calculos (full2 = sin plant_id)
b<-full2 %>% select(Plant_gen_sp,cv_1_fruit, cv_1_seed,cv_1_visitation,S_total,S_mean,log_VR,syncLM)

## Replace Inf and -Inf with NA
b[is.na(b) | b == "Inf"] <- NA 
b[is.na(b) | b == "-Inf"] <- NA 

b <- mutate_all(b, ~replace(., is.na(.), 0))


df_with_plotsb <- b %>%
  group_by(Plant_gen_sp) %>%
  nest() %>%
  mutate(plot = map(data, function(.x) {
    .x  %>%
      cor() %>%
      ggcorrplot::ggcorrplot(show.diag = F, type="lower",lab=TRUE)
  }))


plots1 <- map2(df_with_plotsb$plot, df_with_plotsb$Plant_gen_sp, ~(.x + labs(title = .y)))


ggarrange(plots1[[1]], plots1[[2]], plots1[[3]], plots1[[4]],plots1[[5]],plots1[[6]], plots1[[7]], plots1[[8]], plots1[[9]], plots1[[10]],plots1[[11]],plots1[[12]], ncol=4, nrow=3, common.legend = TRUE, legend="right")

```

\elandscape

\newpage

Data with species in more than 3 sites. I removed 4 plant species (A.fistulosus, C.libanotis, c.monspeliensis, T.fructicans)

Salvia rosmarinus = only one year per site (remove)

Replace Inf and -Inf with NA

We analysed the relationship between fruit proportion stability and visitation rate stability

```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}

# 4 plant species are in 2-3 site (A.fistulosus, C.libanotis, c.monspeliensis, T.fructicans)

# eliminar plant species en new data
sp_out2=full2 %>%
  group_by(Plant_gen_sp) %>%
  summarise(Unique_Id = n_distinct(Site_ID)) %>%
  filter(Unique_Id <= 3) %>%
  select(Plant_gen_sp) %>% pull(Plant_gen_sp)

#Data with species in more than 3 sites
full_2 = full2 %>% filter(!Plant_gen_sp %in% sp_out2)

# Salvia rosmarinus solo un dato por año(estabilidad y sincronia =NA). Eliminar

full_2<-subset(full_2, Plant_gen_sp != 'Salvia rosmarinus')

## Replace Inf and -Inf with NA
full_2[is.na(full_2) | full_2 == "Inf"] <- NA 
full_2[is.na(full_2) | full_2 == "-Inf"] <- NA 


#plot
plots_sta_fruit <- full_2 %>%
  group_by(Plant_gen_sp) %>%
  group_map(~ ggplot(.) + aes(x=cv_1_visitation, y=cv_1_fruit) + 
 theme_bw()+ geom_point(size = 5) + labs(x = "visitation rate  stability",y="fruit proportion stability")+ ggtitle(.y[[1]])+theme(text = element_text(size=18)))

ggarrange(plots_sta_fruit[[1]],plots_sta_fruit[[2]],plots_sta_fruit[[3]],plots_sta_fruit[[4]],plots_sta_fruit[[5]],plots_sta_fruit[[6]],plots_sta_fruit[[7]], ncol=3, nrow=3)

```


Halimium calycinum only one observation



\newpage

Summary of model per plant species

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
 
#model
sta_fruit<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_fruit~cv_1_visitation,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()


opts <- options(knitr.kable.NA = "")

sta_fruit<-sta_fruit %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

sta_fruit %>% 
    kable("latex",booktabs = TRUE, digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(sta_fruit$p.value < 0.05| is.na(sta_fruit$p.value), T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")
```

Goodness of fit measures, p-values for hypothesis tests on residuals, and model convergence information.
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}

#goodness of fit measures, p-values for hypothesis tests on residuals, or model convergence information.
sta_fruit_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_fruit~cv_1_visitation,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

table3<-sta_fruit_glance %>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))
  

table3 %>% 
    kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="left")

```

checking residuals, I detect problems with the homogeneity of variance for all plant species 

\newpage

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

# model plot (fruit proportion stability and visitation rate stability)
sta_fruit.1 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_fruit~cv_1_visitation,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "cv_1_visitation"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))



p1=sta_fruit.1$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  cv_1_visitation, y = cv_1_fruit),shape=20)+ 
  labs(x = "visitation rate stability",y="fruit proportion stability",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p2=sta_fruit.1$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  cv_1_visitation, y = cv_1_fruit),shape=20)+ 
  labs(x = "visitation rate stability",y="fruit proportion stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=sta_fruit.1$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  cv_1_visitation, y = cv_1_fruit),shape=20)+ 
  labs(x = "visitation rate stability",y="fruit proportion stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=sta_fruit.1$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  cv_1_visitation, y = cv_1_fruit),shape=20)+ 
  labs(x = "visitation rate stability",y="fruit proportion stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=sta_fruit.1$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  cv_1_visitation, y = cv_1_fruit),shape=20)+ 
  labs(x = "visitation rate stability",y="fruit proportion stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=sta_fruit.1$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  cv_1_visitation, y = cv_1_fruit),shape=20)+ 
  labs(x = "visitation rate stability",y="fruit proportion stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))


p1+p2+p3+p5+p6+p7

```


\newpage

We analysed the relationship between seed number stability and visitation rate stability

```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}

#plot
plots_sta_seed <- full_2 %>%
  group_by(Plant_gen_sp) %>%
  group_map(~ ggplot(.) + aes(x=cv_1_visitation, y=cv_1_seed) + 
 theme_bw()+ geom_point(size = 5) + labs(x = "visitation rate  stability",y="seed stability")+ ggtitle(.y[[1]])+theme(text = element_text(size=18)))


ggarrange(plots_sta_seed[[1]],plots_sta_seed[[2]],plots_sta_seed[[3]],plots_sta_seed[[4]],plots_sta_seed[[5]],plots_sta_seed[[6]],plots_sta_seed[[7]], ncol=3, nrow=3)

```

\newpage

Summary of model 

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
# Relationship between seed number stability and visitation rate stability

sta_seed<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_seed~cv_1_visitation,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()


opts <- options(knitr.kable.NA = "")

sta_seed<-sta_seed %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

sta_seed %>% 
kable("latex",booktabs = TRUE, digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(sta_seed$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

```

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}

#goodness of fit measures

sta_seed_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_seed~cv_1_visitation,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

table4<-sta_seed_glance %>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Salvia rosmarinus', 'S.rosmarinus', Plant_gen_sp))
  

table4 %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="left")

```

\newpage

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

# model plot (seed number stability and visitation rate stability)
sta_seed.1 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_seed~cv_1_visitation,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "cv_1_visitation"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))



p1=sta_seed.1$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  cv_1_visitation, y = cv_1_seed),shape=20)+ 
  labs(x = "visitation rate stability",y="seed number stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=sta_seed.1$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  cv_1_visitation, y = cv_1_seed),shape=20)+ 
  labs(x = "visitation rate stability",y="seed number stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=sta_seed.1$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  cv_1_visitation, y = cv_1_seed),shape=20)+ 
  labs(x = "visitation rate stability",y="seed number stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=sta_seed.1$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  cv_1_visitation, y = cv_1_seed),shape=20)+ 
  labs(x = "visitation rate stability",y="seed number stability",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=sta_seed.1$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  cv_1_visitation, y = cv_1_seed),shape=20)+ 
  labs(x = "visitation rate stability",y="seed number stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=sta_seed.1$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  cv_1_visitation, y = cv_1_seed),shape=20)+ 
  labs(x = "visitation rate stability",y="seed number stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=sta_seed.1$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  cv_1_visitation, y = cv_1_seed),shape=20)+ 
  labs(x = "visitation rate stability",y="seed number stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

p1+p2+p3+p4+p5+p6+p7
```

\newpage

Relationship between richness-synchrony with different synchrony indice.

A- Total richness ~ log VR

```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}

#plot
plots_rich <- full_2 %>%
  group_by(Plant_gen_sp) %>%
  group_map(~ ggplot(.) + aes(x=log_VR, y=S_total) + 
 theme_bw()+ geom_point(size = 5) + labs(x = "log VR",y="Total richness")+ ggtitle(.y[[1]])+theme(text = element_text(size=18)))


ggarrange(plots_rich[[1]],plots_rich[[2]],plots_rich[[3]],plots_rich[[4]],plots_rich[[5]],plots_rich[[6]],plots_rich[[7]], ncol=3, nrow=3)

```

\newpage

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

rich<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_total~log_VR,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

rich<-rich %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

rich %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(rich$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

```

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}

#goodness of fit measures

rich_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_total~log_VR,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

table5<-rich_glance %>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))

table5 %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="left")

```

\newpage
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

rich.1 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_total~log_VR,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "log_VR"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))



p1=rich.1$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=rich.1$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=rich.1$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=rich.1$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=rich.1$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=rich.1$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=rich.1$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

p1+p2+p3+p4+p5+p6+p7
```


\newpage
B- total richness ~ Loreau & Mazancourt syncrony index
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

rich2<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_total~syncLM,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

rich2<-rich2 %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

rich2 %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(rich2$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

```

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}

#goodness of fit measures
rich2_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_total~syncLM,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

table6<-rich2_glance %>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))

table6 %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="left")

```


\newpage
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

rich.2 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_total~syncLM,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "syncLM"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))



p1=rich.2$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=rich.2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=rich.2$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=rich.2$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=rich.2$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=rich.2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=rich.2$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

p1+p2+p3+p4+p5+p6+p7
```

\newpage

C- mean richness ~ log VR
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

rich3<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_mean~log_VR,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

rich3<-rich3 %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

rich3 %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(rich3$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

```

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}

#goodness of fit measures

rich3_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_mean~log_VR,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

table5<-rich3_glance %>%
  mutate(Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))

table5 %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="left")

```

\newpage
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

rich.3 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_mean~log_VR,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "log_VR"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))


p1=rich.3$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=rich.3$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=rich.3$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=rich.3$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=rich.3$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=rich.3$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=rich.3$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

p1+p2+p3+p4+p5+p6+p7
```

\newpage

D- mean richness ~ Loreau & Mazancourt syncrony index
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

rich4<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_mean~syncLM,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

rich4<-rich4 %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

rich4 %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(rich4$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

```

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}

#goodness of fit measures

rich4_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_mean~syncLM,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

table6<-rich4_glance %>%
  mutate(Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))

table6 %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="left")

```

\newpage
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

rich.4 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_mean~syncLM,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "syncLM"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))


p1=rich.4$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=rich.4$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=rich.4$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=rich.4$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=rich.4$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=rich.4$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=rich.4$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

p1+p2+p3+p4+p5+p6+p7
```

\newpage

We analysed whether the visitation rate stability is affected by richness and synchrony for each plant species separately

A) total richness + log VR
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

#model 1: richness + log VR
sta_polli<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_total+log_VR,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

sta_polli<-sta_polli %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

sta_polli %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = c("","","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(sta_polli$p.value < 0.05| is.na(sta_polli$p.value), T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

```

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}

#goodness of fit measures
sta_polli_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_total+log_VR,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

table7<-sta_polli_glance %>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))

table7 %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="left")

```


\newpage
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

# model plot (cv_1_visitation~richness)
sta_polli2 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_total+log_VR,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_total"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))


p1=sta_polli2$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
  labs(x = "S_total",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=sta_polli2$plots[[2]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer")), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
  labs(x = "S_total",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=sta_polli2$plots[[3]] + geom_point(data = na.omit (full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius")), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
  labs(x = "S_total",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))


p5=sta_polli2$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
  labs(x = "S_total",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=sta_polli2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
  labs(x = "S_total",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))


p1+p2+p3+p5+p6
```


\newpage
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

# model plot (cv_1_visitation~log_VR)
sta_polli2.1 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_total+log_VR,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "log_VR"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))



p1=sta_polli2.1$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ 
  labs(x = "log_VR",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=sta_polli2.1$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ 
  labs(x = "log_VR",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=sta_polli2.1$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ 
  labs(x = "log_VR",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))


p5=sta_polli2.1$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ 
  labs(x = "log_VR",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=sta_polli2.1$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ 
  labs(x = "log_VR",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))


p1+p2+p3+p5+p6
```

\newpage

B) total richness + Lorea and Mazancourt index
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

#model 2: total richness + Lorea and Mazancourt index
sta_polli3<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_total+syncLM,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

sta_polli3<-sta_polli3 %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

sta_polli3 %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = c("","","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(sta_polli3$p.value < 0.05|is.na(sta_polli3$p.value), T, F))%>%
  kable_styling(position="center", latex_option="hold_position")

```

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}

#goodness of fit measures
sta_polli_glance3<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_total+syncLM,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

table8<-sta_polli_glance3 %>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))

table8 %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="left")

```


\newpage
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

# model plot (cv_1_visitation~ total richness)
sta_polli3.1 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_total+syncLM,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_total"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))


p1=sta_polli3.1$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
  labs(x = "S_total",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=sta_polli3.1$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
  labs(x = "S_total",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=sta_polli3.1$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
  labs(x = "S_total",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))


p5=sta_polli3.1$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
  labs(x = "S_total",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=sta_polli3.1$plots[[6]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata")), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
  labs(x = "S_total",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=sta_polli3.1$plots[[7]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas")), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
  labs(x = "S_total",y="visitation rate stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

p1+p2+p3+p5+p6+p7
```


\newpage
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

# model2 plot (cv_1_visitation~syncLM)
sta_polli3.2 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_total+syncLM,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "syncLM"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))



p1=sta_polli3.2$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ 
  labs(x = "syncLM",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=sta_polli3.2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ 
  labs(x = "syncLM",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=sta_polli3.2$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ 
  labs(x = "syncLM",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))


p5=sta_polli3.2$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ 
  labs(x = "syncLM",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=sta_polli3.2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ 
  labs(x = "syncLM",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=sta_polli3.2$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ 
  labs(x = "syncLM",y="visitation rate stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

p1+p2+p3+p5+p6+p7
```

\newpage

C) mean richness + log VR
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

#model 3: mean richness + log VR
sta_polli_Smean<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_mean+log_VR,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

sta_polli_Smean<-sta_polli_Smean %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

sta_polli_Smean %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = c("","","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(sta_polli_Smean$p.value < 0.05|is.na(sta_polli_Smean$p.value), T, F))%>%
  kable_styling(position="center", latex_option="hold_position")

```

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}

#goodness of fit measures
sta_polli_glance_mod3<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_mean+log_VR,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

table9<-sta_polli_glance_mod3 %>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))

table9 %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="left")

```

\newpage
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

# model3 plot (cv_1_visitation~ mean richness)
sta_polli_Smean_plot <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_mean+log_VR,data))) %>%
  mutate(mod = list(ggeffects::ggpredict(mod, terms = "S_mean"))) %>%
  mutate(plots = list(ggplot(mod, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))


p1=sta_polli_Smean_plot$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=sta_polli_Smean_plot$plots[[2]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer")), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=sta_polli_Smean_plot$plots[[3]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius")), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))


p5=sta_polli_Smean_plot$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=sta_polli_Smean_plot$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p1+p2+p3+p5+p6
```


\newpage
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

# model3 plot (cv_1_visitation~log_VR)
sta_polli_Smean_plot2 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_mean+log_VR,data))) %>%
  mutate(mod = list(ggeffects::ggpredict(mod, terms = "log_VR"))) %>%
  mutate(plots = list(ggplot(mod, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))


p1=sta_polli_Smean_plot2$plots[[1]] + geom_point(data =full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ labs(x = "log_VR",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=sta_polli_Smean_plot2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ labs(x = "log_VR",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=sta_polli_Smean_plot2$plots[[3]] + geom_point(data =full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ labs(x = "log_VR",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))


p5=sta_polli_Smean_plot2$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ labs(x = "log_VR",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=sta_polli_Smean_plot2$plots[[6]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata")), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ labs(x = "log_VR",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p1+p2+p3+p5+p6
```


\newpage

D) mean richness + Lorea & Mazancourt index
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

#model 3: mean richness + log VR
sta_polli_Smean2<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_mean+syncLM,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

sta_polli_Smean2<-sta_polli_Smean2 %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

sta_polli_Smean2 %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = c("","","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(sta_polli_Smean2$p.value <0.05|is.na(sta_polli_Smean2$p.value), T, F))%>%
  kable_styling(position="center", latex_option="hold_position")

```

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}

#goodness of fit measures
sta_polli_glance_mod4<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_mean+syncLM,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

table10<-sta_polli_glance_mod4 %>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))

table10 %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="left")

```

\newpage
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

# model4 plot (cv_1_visitation~ mean richness)
sta_polli_Smean_plot4 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_mean+syncLM,data))) %>%
  mutate(mod = list(ggeffects::ggpredict(mod, terms = "S_mean"))) %>%
  mutate(plots = list(ggplot(mod, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))


p1=sta_polli_Smean_plot4$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=sta_polli_Smean_plot4$plots[[2]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer")), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=sta_polli_Smean_plot4$plots[[3]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius")), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))


p5=sta_polli_Smean_plot4$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=sta_polli_Smean_plot4$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=sta_polli_Smean_plot4$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

p1+p2+p3+p5+p6+p7
```


\newpage
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

# model3 plot (cv_1_visitation~syncLM)
sta_polli_Smean_plot4.2 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_mean+syncLM,data))) %>%
  mutate(mod = list(ggeffects::ggpredict(mod, terms = "syncLM"))) %>%
  mutate(plots = list(ggplot(mod, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))


p1=sta_polli_Smean_plot4.2$plots[[1]] + geom_point(data =full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ labs(x = "syncLM",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=sta_polli_Smean_plot4.2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ labs(x = "syncLM",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=sta_polli_Smean_plot4.2$plots[[3]] + geom_point(data =full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ labs(x = "syncLM",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))


p5=sta_polli_Smean_plot4.2$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ labs(x = "syncLM",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=sta_polli_Smean_plot4.2$plots[[6]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata")), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ labs(x = "syncLM",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=sta_polli_Smean_plot4.2$plots[[7]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas")), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ labs(x = "syncLM",y="visitation rate stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

p1+p2+p3+p5+p6+p7
```